Solution-aware vs global ReLU selection: \\ partial MILP strikes back for DNN verification

### 2025-04-08 ATVA 2025/proofsb.tex
update

>>>>

\textcolor{red}{Direct MILP encodings are inefficient! Even the advanced Gurobi MILP solver struggle to sort out all neurons – see Fig11 page27: direct MILP encoding is $>10$ times slower on same instance ($>300s$ vs $<30s$ for similar accuracy) wrt considering only 8 open nodes selected with SAS (more open nodes lead to larger differences). Our main contribution is a way to select the most important nodes, and it helps Gurobi tremendously. This is the whole point of the paper!}
